### 2014-11-12 tex/javalite.tex
Restricted fields to non-primitive types

A Javalite program, $\cfgnt{P}$, is a registry of classes, $\mu$, with
a tuple indicating a class, $\cfgnt{C}$, and a method, $\cfgnt{m}$,
where execution starts. The only primitive type in Javalite is
Boolean. Classes have fields, $([\cfgnt{T}\ \cfgnt{f}]\ ...)$, and
methods, $(\cfgnt{M}\ ...)$. Methods are limited to a single
parameter in our Javalite machine. Expressions, $\cfgnt{e}$, are 
equivalent to a CEKS machine's control string, 
%somewhat typical
where $\cfgt{:=}$ indicates assignment, $\cfgt{=}$ indicates comparison,
and $\cfgt{\$}$ represents the dot-operator for field access. The dot-operator
for method invocation is represented by $\cfgt{@}$. There is no explicit return
statement in Javalite; rather, the value of the last expression is
used as the return value. A variable is always indicated by \cfgnt{x}
and a value by \cfgnt{v}. A value can be a reference in the heap,
$\cfgnt{r}$, or any of the special values shown in~\figref{fig:surface-syntax}. 
We assume that only
type correct programs are given as input to the machine.

>>>>

A Javalite program, $\cfgnt{P}$, is a registry of classes, $\mu$, with
a tuple indicating a class, $\cfgnt{C}$, and a method, $\cfgnt{m}$,
where execution starts. The only primitive type in Javalite is
Boolean. Classes have fields non-primitive, $([\cfgnt{C}\ \cfgnt{f}]\ ...)$, and
methods, $(\cfgnt{M}\ ...)$.\footnote{Summary heaps are able to support non-primitive fields (see \secref{sec:eval}). They are omitted to focus and simplify the presentation.} Methods are limited to a single
parameter in our Javalite machine. Expressions, $\cfgnt{e}$, are 
equivalent to a CEKS machine's control string, 
%somewhat typical
where $\cfgt{:=}$ indicates assignment, $\cfgt{=}$ indicates comparison,
and $\cfgt{\$}$ represents the dot-operator for field access. The dot-operator
for method invocation is represented by $\cfgt{@}$. There is no explicit return
statement in Javalite; rather, the value of the last expression is
used as the return value. A variable is always indicated by \cfgnt{x}
and a value by \cfgnt{v}. A value can be a reference in the heap,
$\cfgnt{r}$, or any of the special values shown in~\figref{fig:surface-syntax}. 
We assume that only
type correct programs are given as input to the machine.
